---
title: "My first post"
author: "Gudmundur Einarsson"
date: 2017-11-07T16:00:00-05:00
categories: ["R", "Machine-Learning"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Starting a blog

The plan is to try to do weekly to monthly blogposts about something interesting I learn. I might also write up technical details about setting something up as a reference for my future self.

I chose to use the [blogdown](https://bookdown.org/yihui/blogdown/) package to manage this blog, with the hugo theme [`purehugo`]('http://dplesca.github.io/purehugo/').

This is not the first time that I start a blog, I also have my own [academic page/blog]('http://www.imm.dtu.dk/~guei/'). I just don't post there regularly. Removing some of the overhead, by managing the content/posts as Rmarkdown documents, will hopefully make me more productive as a blogger.

```{r echo=FALSE}
blogdown::shortcode('tweet', '852205086956818432')
```

```{r cars}
summary(cars)
fit <- lm(dist ~ speed, data = cars)
fit
```

# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
